Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-01 demystify.tex
updates

\subsection{School} Graduating from top universities \emph{that we recognize} helps. For example, if you are an international student and your school is well-known, then it is \emph{``top foreign''}, which is a plus.
However, if we do not know much about schools in your country, then we are uncertain about the quality of your school and likely treat your school as \emph{``unknown foreign''}, which can be a minus point.

Many international students mistakenly believe that their school is well-known, but in fact, it is not (e.g., many Vietnamese students believe that ``Bach Khoa'' is well-known internationally, but it is not).  So you should explicitly mention that in your SOP and ask your LOR writers to do that as well. 
Of course, if you're interested in working with Vietnamese, consider  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{CS programs in the US that have Vietnamese professors}. %It might also be helpful to have your CS dept to put itself on CSRankings so that others know about the dept, its faculty, and research.

>>>>

\subsection{School} Graduating from top universities \emph{that adcom members recognize helps}. For example, if you are an international student and your school is well-known, then it is \emph{``top foreign''}, which is a plus.
However, if we do not know much about schools in your country, then we are uncertain about the quality of your school and likely treat your school as \emph{``unknown foreign''}, which can be a minus point.

Many international students mistakenly believe that their school is well-known, but in fact, it is not, e.g., many Vietnamese students believe that ``Bach Khoa'' is well-known, but it is not (and their confusing acronyms HUST and HCMUT only make it worse).  So if you think your school is well-known, mention it (and back up with some evidence like rankings or awards) in your SOP.  You can ask your LOR writers to talk about your school as well (\autoref{sec:lor-what-to-do}).
Of course, if you're interested in working with Vietnamese, consider  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{CS programs in the US that have Vietnamese professors}. %It might also be helpful to have your CS dept to put itself on CSRankings so that others know about the dept, its faculty, and research.
